---
title: "Custom model example"
author: "Peter Solymos"
date: "January 12, 2016"
output:
  pdf_document:
    keep_tex: no
    number_sections: yes
    toc: no
---

## Motivation

Accounting for model-selection uncertainty when using custom
singing rate and EDR estimates.

I show the singing rate part here, but EDR calculations are similar.
In the end, one has to combine the results to get offsets
as $log(A_{i} \hat{p_{i}} \hat{q_{i}})$ or $log(\hat{A_{i}} \hat{p_{i}})$.

## Simulating the data

I follow here the `cmulti` help page using a removal model
with non-constant singing rate:

```{r}
library(detect)
simfun1 <- function(n = 10, phi = 0.1, c=1, tau=0.8, type="rem") {
    if (type=="dis") {
        Dparts <- matrix(c(0.5, 1, NA,
                      0.5, 1, Inf,
                      1, Inf, NA), 3, 3, byrow=TRUE)
        D <- Dparts[sample.int(3, n, replace=TRUE),]
        CP <- 1-exp(-(D/tau)^2)
    } else {
        Dparts <- matrix(c(5, 10, NA,
                      3, 5, 10,
                      3, 5, NA), 3, 3, byrow=TRUE)
        D <- Dparts[sample.int(3, n, replace=TRUE),]
        CP <- 1-c*exp(-D*phi)
    }
    k <- ncol(D)
    P <- CP - cbind(0, CP[, -k, drop=FALSE])
    Psum <- rowSums(P, na.rm=TRUE)
    PPsum <- P / Psum
    Pok <- !is.na(PPsum)
    N <- rpois(n, 10)
    Y <- matrix(NA, ncol(PPsum), nrow(PPsum))
    Ypre <- sapply(1:n, function(i) rmultinom(1, N, PPsum[i,Pok[i,]]))
    Y[t(Pok)] <- unlist(Ypre)
    Y <- t(Y)
    list(Y=Y, D=D)
}
n <- 200
x1 <- rnorm(n)
X <- cbind(1, x1)
log.phi <- X %*% c(-2,-1)
set.seed(1234)
vv <- simfun1(n=n, phi=exp(cbind(log.phi, log.phi, log.phi)))
```

## Models and weights

Fit some models, so that we can get model weights:

```{r}
## correlated random variable
x2 <- x1 + rnorm(n, 0, 0.5)
x3 <- x2 + rnorm(n, 0, 0.1)
df <- data.frame(x2=x2, x3=x3)
m1 <- cmulti(vv$Y | vv$D ~ 1, df, type="rem")
m2 <- cmulti(vv$Y | vv$D ~ x2, df,  type="rem")
m3 <- cmulti(vv$Y | vv$D ~ x3, df, type="rem")
```

Calculate IC table and model weights

```{r}
aic <- AIC(m1, m2, m3)
aic$dAIC <- aic$AIC - min(aic$AIC)
## this function calculates weights from delta AIC
wfun <- 
function(dAIC) {
    w <- exp(-dAIC/2)
    w/sum(w)
}
aic$w <- wfun(aic$dAIC)
aic
```

## Parametric bootstrap 

We are incorporating weights into a parametric bootstrap framework.

```{r}
R <- 1000
## list of models
mods <- list(m1, m2, m3)
## create model ID vector based on weights
mid <- sample(1:length(mods), R, replace=TRUE, prob=aic$w)
table(mid) / R
round(aic$w, 3)

## output matrix
mat <- matrix(NA, n, R)
library(MASS)
for (i in 1:R) {
    j <- mid[i]
    m <- mods[[j]]
    cf_star <- mvrnorm(1, coef(m), vcov(m))
    MM <- model.matrix(formula(m$formula, lhs=0), m$model)
    mat[,i] <- exp(drop(MM %*% cf_star))
}
```

